Manuscript analyses

### 2022-05-27 ide_cel/Manuscript analyses.Rmd
Add var in tables

## Table S3. Patient characteristics by grade 3+ cytopenia at Day 30
```{r}
cart1 %>% 
  distinct(MRN, .keep_all = TRUE) %>% 
  filter(is.na(Not_evaluable_at_30days)) %>% 
  select(`Circulating Plasma Cells? (yes=1, no=0)`,
         number_prior_lines_therapy,
         `Days from last bridging to CAR-T infusion`,
         "Lenalidomide (exposed=0 vs. refractory=1)",
         "Bortezomib (exposed=0 vs. refractory=1)",
         "Carfilzomib (exposed=0 vs. refractory=1)",
         "Pomalidomide (exposed=0 vs. refractory=1)",
         "Daratumumab (exposed=0 vs. refractory=1)",
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         cytopenia_apheresis,`cytopenia_-5d`,
         `marrow % cellularity day +30`,

         Age, agecat, male_sex, Sex,
         `Extramedullary Disease? (yes=1, no=0)`, 
         `High Marrow Burden? (yes=1, no=0)`, `ECOG at LD (at baseline visit)`, 
         `R-ISS at CAR-T Infusion`, cyto, 
         `Bridging Therapy (Yes=1, No=0)`,
         `Received alkylating therapy with bridging (Yes=1, No=0)`,
         `Prior auto SCT (yes=1, no=0)`, `Prior Allo SCT (Yes=1, No=0)`,
         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes=1, No=0)`,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)`,
         cytopenia_apheresis, `cytopenia_-5d`, gr3_cytopenia_apheresis, `gr3_cytopenia_-5d`,
         `gr3_cytopenia_30d`) %>% 
  tbl_summary(by = `gr3_cytopenia_30d`,
              type = list(
                c(`Extramedullary Disease? (yes=1, no=0)`,
                  `Circulating Plasma Cells? (yes=1, no=0)`,
                  cytopenia_apheresis,`cytopenia_-5d`,
                  cyto,
                  `Bridging Therapy (Yes=1, No=0)`,
                  `Received alkylating therapy with bridging (Yes=1, No=0)`,
                  `Prior auto SCT (yes=1, no=0)`,
                  immuno, proteasome, dara,
                  doubleref, tripleref, pentaref,
                `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)`)
                ~"categorical",
                `marrow % cellularity day +30` ~ "continuous"),

@@

## Table S3. Patient characteristics by grade 3+ cytopenia at Day 90
```{r}
cart1 %>% 
  distinct(MRN, .keep_all = TRUE) %>% 
  filter(is.na(Not_evaluable_at_90days)) %>% 
  select(`Circulating Plasma Cells? (yes=1, no=0)`,
         number_prior_lines_therapy,
         `Days from last bridging to CAR-T infusion`,
         "Lenalidomide (exposed=0 vs. refractory=1)",
         "Bortezomib (exposed=0 vs. refractory=1)",
         "Carfilzomib (exposed=0 vs. refractory=1)",
         "Pomalidomide (exposed=0 vs. refractory=1)",
         "Daratumumab (exposed=0 vs. refractory=1)",
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         cytopenia_apheresis,`cytopenia_-5d`,
         `marrow % cellularity day +90`,
         Age, agecat, male_sex, Sex,
         `Extramedullary Disease? (yes=1, no=0)`, 
         `High Marrow Burden? (yes=1, no=0)`, `ECOG at LD (at baseline visit)`, `R-ISS at CAR-T Infusion`, cyto, 
         `Bridging Therapy (Yes=1, No=0)`,
         `Received alkylating therapy with bridging (Yes=1, No=0)`,
         `Prior auto SCT (yes=1, no=0)`, `Prior Allo SCT (Yes=1, No=0)`,
         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes=1, No=0)`,
         `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)`,
         `gr3_cytopenia_90d`) %>% 
  tbl_summary(by = `gr3_cytopenia_90d`,
              type = list(
                c(`Extramedullary Disease? (yes=1, no=0)`,
                  `Circulating Plasma Cells? (yes=1, no=0)`,
                  cytopenia_apheresis,`cytopenia_-5d`,
                  cyto,
                  `Bridging Therapy (Yes=1, No=0)`,
                  `Received alkylating therapy with bridging (Yes=1, No=0)`,
                  `Prior auto SCT (yes=1, no=0)`,
                  immuno, proteasome, dara,
                  doubleref, tripleref, pentaref,
                  `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)`)
                ~ "categorical",
                `marrow % cellularity day +90` ~ "continuous"),

              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
              digits = all_continuous() ~ 1
  ) %>% 
  bold_labels() %>% add_stat_label() %>%  add_p() %>% 
  modify_footnote(update = everything() ~ NA) %>%
  modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Cytopenia at days 90?**")
```

>>>>

## Table S3. Patient characteristics by grade 3+ cytopenia at Day 30
```{r}
cart1 %>% 
  distinct(MRN, .keep_all = TRUE) %>% 
  filter(is.na(Not_evaluable_at_30days)) %>% 
  select(`Circulating Plasma Cells? (yes=1, no=0)`,
         `Number of prior lines of therapy`,
         number_prior_lines_therapy,
         `Days from last bridging to CAR-T infusion`,
         "Lenalidomide (exposed=0 vs. refractory=1)",
         "Bortezomib (exposed=0 vs. refractory=1)",
         "Carfilzomib (exposed=0 vs. refractory=1)",
         "Pomalidomide (exposed=0 vs. refractory=1)",
         "Daratumumab (exposed=0 vs. refractory=1)",
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         `marrow % cellularity day +30`,

         Age, agecat, male_sex, Sex,
         `Extramedullary Disease? (yes=1, no=0)`, 
         `High Marrow Burden? (yes=1, no=0)`, `ECOG at LD (at baseline visit)`, 
         `R-ISS at CAR-T Infusion`, cyto, 
         `Bridging Therapy (Yes=1, No=0)`,
         `Received alkylating therapy with bridging (Yes=1, No=0)`,
         `Prior auto SCT (yes=1, no=0)`, `Prior Allo SCT (Yes=1, No=0)`,
         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes=1, No=0)`,
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)`,
         cytopenia_apheresis, Neutropenia_apheresis,
         Anemia_apheresis,Thrombocytopenia_apheresis,
         `cytopenia_-5d`, `Neutropenia_-5d`,
         `Anemia_-5d`, `Thrombocytopenia_-5d`,
         gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
         gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
         `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
         `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
         `gr3_cytopenia_30d`) %>% 
  tbl_summary(by = `gr3_cytopenia_30d`,
              type = list(
                c(`Extramedullary Disease? (yes=1, no=0)`,
                  `Circulating Plasma Cells? (yes=1, no=0)`,
                  cytopenia_apheresis,`cytopenia_-5d`,
                  cyto,
                  `Bridging Therapy (Yes=1, No=0)`,
                  `Received alkylating therapy with bridging (Yes=1, No=0)`,
                  `Prior auto SCT (yes=1, no=0)`,
                  immuno, proteasome, dara,
                  doubleref, tripleref, pentaref,
                  cytopenia_apheresis, Neutropenia_apheresis,
                  Anemia_apheresis,Thrombocytopenia_apheresis,
                  `cytopenia_-5d`, `Neutropenia_-5d`,
                  `Anemia_-5d`, `Thrombocytopenia_-5d`,
                  gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
                  gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
                  `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
                  `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
                  `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)`)
                ~"categorical",
                c(`Number of prior lines of therapy`, `marrow % cellularity day +30`)
                ~ "continuous"),

@@

## Table S3. Patient characteristics by grade 3+ cytopenia at Day 90
```{r}
cart1 %>% 
  distinct(MRN, .keep_all = TRUE) %>% 
  filter(is.na(Not_evaluable_at_90days)) %>% 
  select(`Circulating Plasma Cells? (yes=1, no=0)`,
         `Number of prior lines of therapy`,
         number_prior_lines_therapy,
         `Days from last bridging to CAR-T infusion`,
         "Lenalidomide (exposed=0 vs. refractory=1)",
         "Bortezomib (exposed=0 vs. refractory=1)",
         "Carfilzomib (exposed=0 vs. refractory=1)",
         "Pomalidomide (exposed=0 vs. refractory=1)",
         "Daratumumab (exposed=0 vs. refractory=1)",
         immuno, proteasome, dara, doubleref, tripleref, pentaref, 
         `marrow % cellularity day +90`,
         Age, agecat, male_sex, Sex,
         `Extramedullary Disease? (yes=1, no=0)`, 
         `High Marrow Burden? (yes=1, no=0)`, `ECOG at LD (at baseline visit)`, `R-ISS at CAR-T Infusion`, cyto, 
         `Bridging Therapy (Yes=1, No=0)`,
         `Received alkylating therapy with bridging (Yes=1, No=0)`,
         `Prior auto SCT (yes=1, no=0)`, `Prior Allo SCT (Yes=1, No=0)`,
         `Prior treatment with any gene therapy-based therapeutic or investigational cellular therapy or BCMA targeted therapy (Yes=1, No=0)`,
         `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)`,
         cytopenia_apheresis, Neutropenia_apheresis,
         Anemia_apheresis,Thrombocytopenia_apheresis,
         `cytopenia_-5d`, `Neutropenia_-5d`,
         `Anemia_-5d`, `Thrombocytopenia_-5d`,
         gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
         gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
         `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
         `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
         `gr3_cytopenia_90d`) %>% 
  tbl_summary(by = `gr3_cytopenia_90d`,
              type = list(
                c(`Extramedullary Disease? (yes=1, no=0)`,
                  `Circulating Plasma Cells? (yes=1, no=0)`,
                  cytopenia_apheresis,`cytopenia_-5d`,
                  cyto,
                  `Bridging Therapy (Yes=1, No=0)`,
                  `Received alkylating therapy with bridging (Yes=1, No=0)`,
                  `Prior auto SCT (yes=1, no=0)`,
                  immuno, proteasome, dara,
                  doubleref, tripleref, pentaref,
                  cytopenia_apheresis, Neutropenia_apheresis,
                  Anemia_apheresis,Thrombocytopenia_apheresis,
                  `cytopenia_-5d`, `Neutropenia_-5d`,
                  `Anemia_-5d`, `Thrombocytopenia_-5d`,
                  gr3_cytopenia_apheresis, gr3_Neutropenia_apheresis,
                  gr3_Anemia_apheresis, gr3_Thrombocytopenia_apheresis,
                  `gr3_cytopenia_-5d`, `gr3_Neutropenia_-5d`,
                  `gr3_Anemia_-5d`, `gr3_Thrombocytopenia_-5d`,
                  `Did patient meet eligibility criteria for KarMMa 1 on the day of apheresis (Yes=1, No=0)`)
                ~ "categorical",
                c(`Number of prior lines of therapy`, `marrow % cellularity day +90`)
                ~ "continuous"),
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
              digits = all_continuous() ~ 1
  ) %>% 
  bold_labels() %>% add_stat_label() %>%  add_p() %>% 
  modify_footnote(update = everything() ~ NA) %>%
  modify_spanning_header(all_stat_cols() ~ "**Grade 3+ Cytopenia at days 90?**")
```
